---
title: 'Class 11: Scraping Multiple Webpages'
author: "Ella O'Neall"
date: "2026-09-30"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_download: TRUE
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives for Today

- Scrape multiple webpages using `for` loops;

- Scrape multiple webpages using the  purrr::map()` type functions, which would also make you write your own custom functions in R.

## Extending the Course Buleetin Scrape for multiple departments

For the sake of this example, let us scrape the following pages:
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/) and [MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/)

Note that if you are doing it for just a few departments, you can just repeat your code a few time; however, this is bad practice so we will not do this in class.
Software engineers tend to refer to this as: **DRY** (do not repeat yourself).

```{r bulletin}
dept_abbr = c('acc', 'bus', 'isa', 'mkt') # extending the example to 4 depts

# line below illustrates how the url can be constructed by pasting0(i.e., no space) the base_url, dept_abbreviation, and the forward slash


courses_df = data.frame() # initialize the container

for(dept_name in dept_abbr){
  cat(rep("-", 25))
  print(dept_name)
  dept_url = paste0(
    "https://bulletin.miamioh.edu/courses-instruction/", dept_name, "/")
  
  # for the titles, I will use the selector gadget and for the desc, I will Use the inspector (to show you alternative CSS selectors for what we did on Mon)
  
  webpage = rvest::read_html(dept_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div > p.courseblockdesc") |>
    rvest::html_text2() -> descs
  
  df= data.frame(title = titles, desc = descs)
  df$title[1] |> print() # showing only the first course title
  
  courses_df = rbind(courses_df, df)
  cat(rep("-", 25))
  print("\n")
}


```


## Re-Examining the Prior Example with the `purrr` package

My preferred approach with the purr function is to first create my own function and then use it within the package.

```{r}
scrape_mu_bulletin = function(dept_url){
  
  webpage = rvest::read_html(dept_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div > p.courseblockdesc") |>
    rvest::html_text2() -> descs
  
  df= data.frame(title = titles, desc = descs)
  
  return(df)
}

test = scrape_mu_bulletin("https://bulletin.miamioh.edu/courses-instruction/bus/")

dept_abbr = c('acc', 'bus', 'isa', 'mkt')

my_urls = paste0("https://bulletin.miamioh.edu/courses-instruction/", # single chr string
                 dept_abbr, # vector of four obs
                 "/" # single chr string
                 )

# the map functions take one or more inputs (depending on the function you are using)
# in this example, we only have 1 input for our function
# so we used map_() instead of map2_(), [2 is if you have two inputs], p_map() [for three or more inputs]
# .x = the vector you are iterating over
courses_df_from_purr = purrr::map_df(.x = my_urls, .f = scrape_mu_bulletin)

head(courses_df_from_purr)
```
